signalHsmm - a novel semi-Markov model of eukaryotic signal peptides

### 2015-06-17 paper.tex
added two best groups

\begin{figure}[ht]\centering
\includegraphics[width=0.9\textwidth]{figures/cvres.png}
\caption{Results of cross-validation. 1. An encoding providing the best sensitivity (AUC = 0.9346, MCC = 0.6479). 3. An encoding providing the best specificity (AUC = 0.9687, MCC = 0.8689).}
\label{fig:cvres}
\end{figure}

@@

As the performance measure interest we choose

@@

>>>>

@@

@@

\begin{figure}[ht]\centering
\includegraphics[width=0.9\textwidth]{figures/cvres.png}
\caption{Results of cross-validation. 1. An encoding providing the best sensitivity (AUC = 0.9687, MCC = 0.8689). 2. An encoding providing the best specificity (AUC = 0.9346, MCC = 0.6479).}
\label{fig:cvres}
\end{figure}

We used four performance measures to evaluate results of cross-validation: specificity, sensitivity, Matthew's Correlation Coefficient ($\phi$ coefficient) and Area Under the Curve (AUC). All encodings provide very good AUC (0.93 -- 0.97) and specificity (0.92 -- 0.96). The encodings have the biggest impact on sensitivity, which ranges from 0.66 to 0.94. The final signalHsmm algorithm uses the encoding, that yields the highest specificity and Matthew's Correlation coefficient as well as the second best AUC (see Fig.~\ref{fig:cvres}).

\begin{table}[ht]
\begin{minipage}{.5\linewidth} 
\centering
\begin{tabular}{l}
  \toprule
Groups \\ 
  \midrule
A, E, K, Q, R \\ 
   \rowcolor[gray]{0.85}D, G, N, P, S, T \\ 
  C, H, I, L, M, V \\ 
   \rowcolor[gray]{0.85}F, W, Y \\ 
   \bottomrule
\end{tabular}
\caption{Best-sensitivity (final) encoding} 
\label{tab:best}
\end{minipage}
\begin{minipage}{.5\linewidth} 
\centering
\begin{tabular}{l}
  \toprule
Groups \\ 
  \midrule
A, C \\ 
   \rowcolor[gray]{0.85}D, E, H, K, N, Q, R \\ 
  G, P, S, T, Y \\ 
   \rowcolor[gray]{0.85}F, I, L, M, V, W \\ 
   \bottomrule
\end{tabular}
\caption{Best-specificity encoding} 
\label{tab:worst}
\end{minipage}
\end{table}
